---
title       : Tutorial 1- Getting Started
subtitle    : DPI R Bootcamp / 2013
author      : Jared Knowles
job         : Research Analyst, Wisconsin DPI
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight  # {highlight.js, prettify, highlight}
hitheme     : hemisu-light      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
---

<style>
em {
  font-style: italic
}
strong {
  font-weight: bold;
}
</style>

```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(fig.path='figure/slides-', cache.path='cache/slides-', cache=TRUE,
               comment=NA)
# upload images automatically
#opts_knit$set(upload.fun = imgur_upload)
```

## Self-help (2)
- Sometimes R Help can be a bit prickly and unfriendly...
- The most important part of getting help is being able to ask your question with a reproducible example (i.e. some short simulated data and code that doesn't do what you want)
- Like this:

```{r echo=TRUE,error=TRUE}
foo<-c(1,"b",5,7,0)
bar<-c(1,2,3,4,5)
foo+bar
```

- For R Help etiquette (for the tough problems) see [the great advice here](https://github.com/hadley/devtools/wiki/Reproducibility)

---

## Plot Student Attributes

```{r}
require(eeptools)

qplot(readSS,mathSS,data=stulevel,geom='point',alpha=I(0.3))+theme_dpi()+
  labs(title='Test Score Relationship')+
  geom_smooth()

```